---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# YlGrBlPal

<!-- badges: start -->
<!-- badges: end -->

YlGrBlPal provides a set of colors including Yellow, Green, Turquoise, Indigo and Blue that can be applied to ggplot2 plot. It can be used in discrete-scale color and fill or continuous-scale color.

## Installation

It can be installed through the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2021/r-package-takehome-ShaineHo")
```


## Examples
There are some basic examples which show you how to solve common problems. The packages required for the examples are as follow.  The data of the example is from `palmerpenguins` package. 

```{r example}
library(YlGrBlPal)
library(ggplot2)
library(palmerpenguins)
```


### Example for YlGrBl palette

```{r ylgrbl-pal}
 ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
 geom_point(color = YlGrBl_pal()(1))+
   theme_bw()+
   labs(x = "Flipper length (mm)",
        y = "Body Mass (gram)",
        title = "Relationship between body mass and flipper length of the penguins")
```

### Example for discrete-scale

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
geom_point(aes(color = species))+
scale_colour_YlGrBl_d()+
  theme_bw()+
  labs(x = "Flipper length (mm)",
        y = "Body Mass (gram)",
        title = "Relationship between body mass and flipper length of the penguins by species")
```

